Introduction to Causal Inference Models

### 2017-08-01 msm_introduction.Rmd
updated some stuff

Trying to replicate example in sas code.
```{r}
y_mod <- glm(Y ~ A1 + Z1 + A0 + A1*A0, data = td_sim_data, family = "gaussian")
z1_mod <- glm(Z1 ~ A0, data = td_sim_data, family = "binomial"(link="logit"))
a1_mod <- glm(A1 ~ Z1, data = td_sim_data, family = "binomial"(link="logit"))

@@

>>>>

Trying to replicate simple substitution example in sas code.
```{r}
# g formula
y_mod <- glm(Y ~ A1 + Z1 + A0 + A1*A0, data = td_sim_data, family = "gaussian")
z1_mod <- glm(Z1 ~ A0, data = td_sim_data, family = "binomial"(link="logit"))
a1_mod <- glm(A1 ~ Z1, data = td_sim_data, family = "binomial"(link="logit"))

@@

# creating a formula. will need dplyr
g.formula.td <- function(data, y, a0, a1, z1, y.model, y.family,
  a1.model, a1.family, z1.model, z1.family, estimate = "diff"){

  un_exp_df <- exp_df <- data
  un_exp_df[,c(a0,a1)] <- 0
  exp_df[, c(a0,a1)] <- 1

  # define y.model
  q_mod <- glm(as.formula(paste(y, y.model, sep = "~")), data = data, 
    family = y.family)
  # define z1.model
  z1_mod <- glm(as.formula(paste(z1, z1.model, sep = "~")), data = data, 
    family = z1.family)
  # define a1.model
  a1_mod <- glm(as.formula(paste(a1, a1.model, sep = "~")), data = data, 
              family = a1.family) 
  # updated probability of z1 given a0 = 1
  z1_exp_pr <- mean(predict(z1_mod, newdata = exp_df, type = "response"))
  # simulate vector of new Z1 values accounting for prior A0 where everyone is exposed
  z1_exp_vec <- as.numeric(ifelse(rbinom(n = nrow(data),size = 1 , z1_exp_pr)==T,1,0))
  # update z value under a0=1 scenario
  exp_df[,z1] <- z1_exp_vec
  # update y estimate as if everyone was exposed
  y_exp <- mean(predict(y_mod,newdata=exp_df,type = "response"))

  # updated probability of z1 given a0 = 0
  z1_unexp_pr <- mean(predict(z1_mod, newdata = un_exp_df, type = "response"))
  # simualte vector of new Z1 values accounting for prior A0 where everyone is unexposed
  z1_unexp_vec <- as.numeric(ifelse(rbinom(n = nrow(data), size = 1, z1_unexp_pr)==T,1,0))
  un_exp_df[,z1] <- z1_unexp_vec
  # udpate y estimates as if everyone was unexposed
  y_unexp <- mean(predict(y_mod,newdata=un_exp_df,type = "response"))

  if(estimate == "diff"){ 
    msm_estimate <- y_exp - y_unexp
    }
  if(estimate == "ratio"){
    msm_estimate <- y_exp/y_unexp
  }
  return(msm_estimate)
  }

g.formula.td(data = td_sim_data, y = "Y", a0 = "A0", a1= "A1", z1 = "Z1",
  y.model = "A0+A1+Z1+A0*A1", y.family = "gaussian", a1.model = "Z1", 
  a1.family = "binomial", z1.model = "A0", z1.family = "binomial", estimate = "diff")
